Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-01-17 tex/test-WW-type-00s-PS.tex
jlab

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  
	\caption{\label{aul_jlab} 
	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $  at typical kinematics 
	of COMPASS, 
	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$.
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
\newpage
%========= SECTION 8: TWIST-3 IN WW-TYPE APPROXIMATION ===============
\section{Subleading twist asymmetries in WW-type approximation}
\label{Sec-7:twist-3-and-WW}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (a)
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (b)
\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ , comparison to HERMES data \cite{Airapetian:2005jc} (a), and predictions for COMPASS (b).
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The application of the WW-type approximation (\ref{Eq:WW-type-last}) 
for $h^q(x)$ is subtle. Applying it literally would imply 
$x\,h^q(x) = - 2\,h_1^{\perp(1)}(x)$ at variance with the sum rule
(\ref{Eq:sum-rules-T-odd}) for the collinear T-odd twist-3 TMD $h^q(x)$.
The situation is analog to the case of $f_T^q(x,\kperp)$
discussed in Sec.~\ref{Sec-7.6:FUTsinphiS}. Also here one could introduce
an additional Gauss parameter and use a double Gaussian to describe 
$h^q(x,\kperp)$. One should keep this in mind as an interesting possibility
to be explored in future studies. However, at this point we have no guidance
from theory or phenomenology to fix additional parameters. We therefore
proceed analogously to Sec.~\ref{Sec-7.7:FUUcosphi}, and impose 
(in a model-dependent step) the sum rule (\ref{Eq:sum-rules-T-odd}) 
by setting 
\begin{subequations}\be
	x\,h_1^q(x) = 0\,.
\ee

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_COMPASS_x.pdf}  (a)
\includegraphics[width=0.45\textwidth]{\FigPath/AULsin2phi_JLAB_x.pdf}  (b)
	\caption{\label{aul_jlab} 
	$A_{UL}^{\sin(2\phi_h)}$  as a function of $ x $  at typical kinematics 
	of COMPASS, 
	$\la x\ra = 0.05$, $\la z\ra = 0.36$, $\la Q^2\ra = 2.4$ GeV$^2$ (a) and comparison to JLab (b).
	}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
\newpage
%========= SECTION 8: TWIST-3 IN WW-TYPE APPROXIMATION ===============
\section{Subleading twist asymmetries in WW-type approximation}
\label{Sec-7:twist-3-and-WW}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (a)
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (b)
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_JLAB_x.pdf} (c)
\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ , comparison to HERMES data \cite{Airapetian:2005jc} (a), and predictions for COMPASS (b), and comparison to JLab (c).
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The application of the WW-type approximation (\ref{Eq:WW-type-last}) 
for $h^q(x)$ is subtle. Applying it literally would imply 
$x\,h^q(x) = - 2\,h_1^{\perp(1)}(x)$ at variance with the sum rule
(\ref{Eq:sum-rules-T-odd}) for the collinear T-odd twist-3 TMD $h^q(x)$.
The situation is analog to the case of $f_T^q(x,\kperp)$
discussed in Sec.~\ref{Sec-7.6:FUTsinphiS}. Also here one could introduce
an additional Gauss parameter and use a double Gaussian to describe 
$h^q(x,\kperp)$. One should keep this in mind as an interesting possibility
to be explored in future studies. However, at this point we have no guidance
from theory or phenomenology to fix additional parameters. We therefore
proceed analogously to Sec.~\ref{Sec-7.7:FUUcosphi}, and impose 
(in a model-dependent step) the sum rule (\ref{Eq:sum-rules-T-odd}) 
by setting 
\begin{subequations}\be
	x\,h^q(x) = 0\,.
\ee
